---
title: "Structural similarity between graphs"
author: "nikitha"
date: "23 December 2017"
output: html_document
---



## R Markdown
Finding the similarity between the 2 models having similar component name but change in relationship type.
get to know the idea by comparing 2 similarity matrix, which node has the difference in edge structure or which components have different edge structure.
Association between 2 matrices can be calculated using corelation test.(cor.test) 


#read dataset of 2 model
```{r}
#read data of version 3 airport model 
library(readr)
elements1 <- read_csv("H:/theis_work/SWC_chair_ml_related/Archi_data/03airport_version3/elements.csv")
dim(elements1)

library(readr)
relations1 <- read_csv("H:/theis_work/SWC_chair_ml_related/Archi_data/03airport_version3/relations.csv")
dim(relations1)

#read data of changed airport model of version3(removed/added edge data)
library(readr)
elements2 <- read_csv("H:/theis_work/SWC_chair_ml_related/02_work/02case_study_graph_analytics/version3_AIRPORT/V3_cs10_GA_structural_similarity/archiData/elements.csv")
dim(elements2)

library(readr)
relations2 <- read_csv("H:/theis_work/SWC_chair_ml_related/02_work/02case_study_graph_analytics/version3_AIRPORT/V3_cs10_GA_structural_similarity/archiData/relations.csv")
dim(relations2)

```

###case study to find structural similarity between the models having similar component name/ similar no of components
#produce graph 1
```{r}
#produce graph1 fro, version 3 originalc

h<-elements1[match(relations1$Source, elements1$ID), 3, drop=F]
g<-elements1[match(relations1$Target, elements1$ID), 3, drop=F]

j<-cbind(h,g)   #new dataframe

#change column names
colnames(j)[1] <- "new_source"
colnames(j)[2] <- "new_target"

#combine with the relation table
dat<-cbind(relations1, j)


dat$Source<- NULL
dat$Target<- NULL

library(igraph)
col<-dat[, 5:6]
eg1 <- graph_from_data_frame(col, directed = TRUE)
plot(eg1)
```

#produce graph 2
```{r}
#produce graph2 from version 3 alterations model

h<-elements2[match(relations2$Source, elements2$ID), 3, drop=F]
g<-elements2[match(relations2$Target, elements2$ID), 3, drop=F]

j<-cbind(h,g)   #new dataframe

#change column names
colnames(j)[1] <- "new_source"
colnames(j)[2] <- "new_target"

#combine with the relation table
dat<-cbind(relations2, j)


dat$Source<- NULL
dat$Target<- NULL

library(igraph)
col<-dat[, 5:6]
eg2<- graph_from_data_frame(col, directed = TRUE)
plot(eg2)
```

```{r}
#findinf similarity using jaccard index
sim1<- similarity.jaccard(eg1, mode = "out")
sim2<- similarity.jaccard(eg2, mode="out")

#finding corellation between 2 similarity matrix
assoc_sim<- cor.test(sim1, sim2)
assoc_sim
#or
cor1<- diag(cor(sim1,sim2))
```


```{r}


#findinf similarity using dice index
sim1_d<- similarity.dice(eg1, mode = "out")
sim2_d<- similarity.dice(eg2, mode="out")

#finding corellation between 2 similarity matrix
assoc_sim<- cor.test(sim1_d, sim2_d)
assoc_sim
#or
cor2<-diag(cor(sim1_d,sim2_d))
```

##matrix equality
#match the matrices
matequal <- function(x, y)
    is.matrix(x) && is.matrix(y) && dim(x) == dim(y) && all(x == y)
matequal(sim1, sim2)


##extra
cor1<- as.matrix(cor1)
cor2<- as.matrix(cor2)
cor(cor1, cor2)

d1<- sim2(sim1, sim2)
d1_d<- sim2(sim1_d, sim2_d)
cor.test(d1, d1_d)
###it shows thar similarity found by 2 metrics results in almost equal result. so we decide to use jaccard over dice.
##inverse log doesnot suits well for directed graph

###plot is remaining
